---
title: "Pokemon App"
author: "Camila San Jose"
date: "11/3/2020"
output: pdf_document
params: 
  selpok: ["Charmander", "Jigglypuff"]
  selvar: ["1"]
---

```{r setup, include=FALSE, warning=F, message=FALSE}
library(shiny)
library(tidyverse)
library(shinyjs)
library(plotly)
library(shinythemes)
library(httr)
library(dplyr)
library(shinyjs)
library(reshape2)
library(shinydashboard)
library(htmltools)

#Get data from the web

url<- "https://pokemon-go1.p.rapidapi.com/pokemon_stats.json"
key = "11a0831306msh85289b71ee29d28p1b0d2ajsnd56ec6de06bd"
pokemon = GET(url, config=add_headers("x-rapidapi-host"= "pokemon-go1.p.rapidapi.com",'x-rapidapi-key' = key))


details<- httr::content(pokemon,as='parsed')
details

##########################################################################
#cleaning, manipulation and analysis of the retrieved data

attack <- numeric(length(details))
defense<- numeric(length(details))
stamina <- numeric(length(details))
formas <- numeric(length(details))
id <- numeric(length(details))
name <- numeric(length(details))

for (i in 1:length(details)) {
    attack[i] <- as.numeric(details[[i]]$base_attack)
    defense[i] <- as.numeric(details[[i]]$base_defense)
    stamina[i] <- as.numeric(details[[i]]$base_stamina)
    formas<- details[[i]]$form
    id[i] <- as.numeric(details[[i]]$pokemon_id)
    name[i] <- details[[i]]$pokemon_name
}

data<- as.data.frame(cbind(id, name, formas, stamina, defense, attack))
data<- distinct(data)

data_name<- sort(data$name)
data_var <- c("stamina"=1, "defense"=2, "attack"=3)
dataplot <- melt(data=data, id.vars= "name", measure.vars=c("stamina", "defense", "attack"))
data2<- data[,3:5]
d<- as.numeric(as.character(data2[,1]))
dd<- as.numeric(as.character(data2[,2]))
ddd<- as.numeric(as.character(data2[,3]))
data2<- cbind(d,dd,ddd)
c=as.data.frame(data2)
a=cbind(data[,2],c)
names(a)<-c("name","stamina", "defense", "attack") 

data_filtered <-
        a %>% filter(name %in% params$selpok)
    
data_filtered2 <- 
        dataplot %>% filter(name %in% params$selpok)

```

# Introduction

This report is dynamic, which means it will show you the variables you have selected from the Shiny App. 

# Selection of Data

These are the Pokemon you selected to compare: 
```{r, echo=F}
params$selpok
```

The variable that you chose to create the histogram was: 
```{r, echo=F}
params$selvar
```


## Plots

The plots that are generated from the Pokemon you selected to compare is the following: 

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height= 5}

ggplot(data_filtered2, aes(x=variable, y= value, color=name, group= name))+ 
           geom_line()+ labs(color= "Pokemon selected")
```

The plot of the variable you selected is:

```{r, echo=FALSE, warning=FALSE, message=FALSE}
varsel= as.numeric(params$selvar)

ggplot(c, aes(c[,varsel])) +
        geom_histogram(fill="lightblue", col="darkgoldenrod1")+ labs(title= paste("Histogram of ", names(data_var[varsel]))) + xlab( names(data_var[varsel]))
```



Thank your for interacting with the Pokemon! I hope you enjoyed! 

